%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Copyright (c) 2011 QUALCOMM Incorporated. All rights reserved. 
% Qualcomm Confidential and Proprietary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This LaTeX template file includes the current Qualcomm legal restricted distribution statement 
% along with the appropriate Qualcomm address for this document, which appears on the document 
% cover. This file is pulled into the 'titlepage.tex' file during the LaTeX document
% build and must reside in the the /dox/latex folder. If the legal statement is changed by 
% Legal, all Doxygen/LaTeX users will be notified to replace this file. 
%
% To ensure that the PDF produced using this template file meets the Qualcomm document 
% formatting standards, except for the copyright date, please do not change this file. For
% information about the Living Docs Project, select go/livingdocs
%
% Author: Lori Boyters, Living Docs Technical Lead. 
% LaTeX templates are maintained in Perforce by the Living Docs team. As updates are made, 
% Doxygen/LaTeX users will be notified to update their templates. If you would like to be 
% notified when updates occur, send email to livingdocs.support.
%
% Updated 05/28/2010 Rev B Version 6 for Doxygen 1.5.9
% Updated 09/22/2010 Rev C Version 1 for Doxygen 1.7.0
% Updated 09/28/2010 Rev C Version 2 (interim)
% Updated 01/28/2011 Rev C Version 2 (see Release Notes for details)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace*{0.1pt}
\begin{center}
\bf\large Qualcomm Confidential and Proprietary
\end{center}
\vspace*{-0.1pt}
\begin{justifying}
\setlength{\parskip}{2ex plus 1ex minus 2ex}
\small \textbf{Restricted Distribution.} \small Not to be distributed to anyone who is not an employee of either Qualcomm or a subsidiary of Qualcomm without the express approval of Qualcomm's Configuration Management.

\noindent Not to be used, copied, reproduced in whole or in part, nor its contents revealed in any manner to others without the express written permission of Qualcomm.

\noindent Qualcomm reserves the right to make changes to the product(s) or information contained herein without notice. No liability is assumed for any damages arising directly or indirectly by their use or application. The information provided in this document is provided on an ``as is'' basis.

\noindent This document contains Qualcomm confidential and proprietary information and must be shredded when discarded.

\noindent QUALCOMM is a registered trademark of QUALCOMM Incorporated in the United States and may be registered in other countries. Other product and brand names may be trademarks or registered trademarks of their respective owners. CDMA2000 is a registered certification mark of the Telecommunications Industry Association, used under license. ARM is a registered trademark of ARM Limited. QDSP is a registered trademark of QUALCOMM Incorporated in the United States and other countries.

\noindent This technical data may be subject to U.S. and international export, re-export, or transfer (export) laws. Diversion contrary to U.S. and international law is strictly prohibited.
\end{justifying}
\vspace{-0.04pt}
\bf\begin {center}
QUALCOMM Incorporated \\
5775 Morehouse Drive \\
San Diego, CA 92121-1714 \\
U.S.A. \\
\vspace{0.01pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Change the copyright date to reflect the year(s) this document was published. For 
% example, if Rev A was published in 2009, and this is now Rev B to be published in 2010, 
% change the copyright date only from "2010" to "2009-2010".
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Copyright \copyright \ 2011 QUALCOMM Incorporated. \\
All rights reserved. \\
\end{center}


